Exploratory_Analysis_Josh_Tobey

### 2025-12-08 Exploratory_Analysis_Josh_Tobey.Rmd

```
```{r}
summary(exploratory_df)

@@

```
```{r}
exploratory_df$Timestamp <- ymd(exploratory_df$Timestamp)
exploratory_df <- exploratory_df[order(exploratory_df$Timestamp), ]
ggplot(exploratory_df, aes(x = Timestamp,
                           y = mean_Temp,
                           color = mean_Temp)) +
  geom_line() + 
  scale_color_gradient(low = 'yellow', high = 'green')

```
```{r}
library(patchwork)
plot1 <- ggplot(exploratory_df, aes(x = Timestamp,
                           y = mean_pH,
                           color = mean_pH)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red') +
  theme_minimal() +
  ggtitle("Average pH over Time")

>>>>

@@

```{r}
library(patchwork)
plot1 <- ggplot(exploratory_df, aes(x = Timestamp,
                           y = mean_pH,
                           color = mean_pH)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red') +
  theme_minimal() +
  ggtitle("Average pH over Time")
